---
title: "Getting Started with LICHospitalR"
subtlte: Data Analysis and Workflow
author: "Steven P. Sanderson II, MPH"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true 
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Getting Started with LICHospitalR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 4.5,
  fig.align = 'center',
  out.width = '95%',
  dpi = 100
)
```

> LICHospitalR: A toolkit for working with hospital data in R

The data landscape at the hospital is vast, deep, and complex causing many inconsistencies in data attributes and formats ultimately making it difficult to analyze.

The `LICHospitalR` package provides tools that solve these issues.

* __DB Data Functions__: `coded_consults_query` is one such function that fixes this issue.
* __Plot Functions__: `coded_consults_trend_plt`, `coded_consults_top_plt` are some functions that render plots easily and in expected fashion.

This vignette includes a brief case study on getting data on and plotting out coded consults.

# Prerequisites

To get started with LICHospitalR you need to install the library from is source
or binary file.

Once it is installed you can call the library from within R like so:
```{r setup}
library(LICHospitalR)
```
